Characterizing Stellar Streams by ML

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

        \autoref{sec:results_mock:model}

        \todo[inline]{rephrase, this is quoting from the mock stream}
        We select on-stream and off-stream regions using the known
        $\phi_1,\phi_2$ range of the stream. The upper panel of
        \autoref{fig:gd1-photometric_background_selection} shows these
        selections in blue and black, respectively.  The lower panel shows the
        on and off-stream selections in photometric coordinates. An isochrone is
        apparent in the distribution.  We use the off-stream population to train
        a conditional normalizing flow (see
        \autoref{sub:method:photometric_model:off_stream}) on the magnitudes $g$
        and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
        non-parametric distribution characterizing the photometric background,
        including its variation over $\phi_1$.

>>>>

        The modeling framework, detailed in the \autoref{sec:method} sections, is
        modular, allowing many model components to be combined, nested, added
        to the mixture, and linked via priors.
        The model we require for \stream{GD-1} is similar to 
        the model built for the mock stream in \autoref{sec:results_mock:model},
        but has additional components for \stream{GD-1}'s spur.
        In this section we will discuss how the total model is built, noting 
        similarities to the example mocks-stream model.

        All full Bayesian stream models necessarily include a background model,
        which we model in both astrometric and photometric spaces.
        The photometric background is too complex to capture with simple analytic
        distributions. Instead, we train a normalizing flow on the magnitudes $g, r$,
        conditioned on $\phi_1$. We refer readers to
        \autoref{sub:method:photometric_model:off_stream} for discussion of the photometric distribution and how a normalizing flow
        can characterize this complex distribution, including its variation over $\phi_1$.
        The flow's flexibility, while necessary in this context, also poses
        a problem: the flow captures the stream as easily as the background.
        Consequently we select on-stream and off-stream regions using the known
        $\phi_1,\phi_2$ range of the stream, as shown in the
        upper panel of \autoref{fig:gd1-photometric_background_selection}.
        In the lower panel are plotted these selections in photometric coordinates,
        where an isochrone is apparent in the on-stream selection.
        The normalizing flow is trained on the off-stream selection, and will be
        fixed when incorporated into the larger model.

        One part of the larger model is the astrometric component of the background.
        Unlike for the photometry, the background may be fit with simple analytic
        distributions. We use an exponential distribution (see \autoref{sub:exponential_distribution})
